%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Director of Product \& Co-Founder} % Job title
    {AI Squared} % Organisation
    {Boston, Ma} % Location
    {Sept 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item{Own the entire lifecycle of SaaS and PaaS products, responsible for ~\$1 Million Seed Stage ARR.}
        \item{Utilize design thinking and data analytics to guide product design, and aligned implementation with agile methodology.}
        \item{Create and aligned product roadmap to fit product-led-growth and enterprise sales strategies.}        
        \item{Support GTM \& fundraising with tight collaboration with marketing and sales, contributing to a projected \$6 Million revenue pipeline.}
        \item{Create user guides \& documentation and thought leadership articles, and presented at industry-leading conferences.}
        \item{Contribute to and manage an AI development framework (BeyondML), which was accepted to the Linux Foundation as a Sandbox project.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Science Intern} % Job title
    {Maxar Technologies} % Organisation
    {Herndon, Va} % Location
    {May 2021 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Applied computer vision and advanced mapping techniques to COVID-19 risk modeling.}
        \item {Identified and reported to leadership on capabilities gaps and opportunities for intrapreneurship identified through 50 discovery interviews.}
        %experienced the end-to-end process of applying machine learning to answering questions of interest, including through the use of cloud compute on terabyte-scale data sets.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Research \& Teaching Assistant} % Job title
    {University of Delaware} % Organisation
    {Newark, DE} % Location
    {Jun 2017 - Jun 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Utilized virtual reality immersion techniques and computational data analysis in clinical neuroscience research.}
        \item {Instructed 4 semesters of undergraduate students in lecture and lab components of \textit{KAAP 428: Motor Control and Learning.}}
        %with consistently high student evaluations
      \end{cvitems}
    }

\end{cventries}
